Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-02 paper/EDA.qmd
Updates Install Package file
Assumption check complete recovered file

@@

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)
library(performance)

@@

```{r}
#| include: false
#| warning: false
#| message: false
# Barlett Test Homegenity of Variance: testing for ass
# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
# print(bartlett_test)
```

@@

# Check Model Assumptions
check_model(model_b, check = c("normality", "homogeneity"))
```

# Check Model Assumptions
check_model(model, check = c("normality", "homogeneity"))
```

>>>>

# install.packages(c("tidyverse", "janitor", "here", "lubridate", "arrow", "dplyr", 
#   "knitr", "performance", "kableExtra", #"ggpubr"))

@@

library(tidyverse)
library(janitor)
library(here)
library(lubridate)
library(arrow)
library(dplyr)
library(knitr)
library(performance)
library(kableExtra)
library(performance)
library(ggpubr)

@@

# Note from pdf
"In the performance package, it would alert you in red if any assumptions were heavily violated. If you noticed
any, it would be useful to mention them.
Unfortunately it is hard to create non-parametric versions. So if there is a violation for the sake of this
course it is fine to mention there is a violation but you will proceed as if everything was fine."

# Check Model Assumptions
check_model(model, check = c("normality", "homogeneity"))

```{r}
#| include: false
#| warning: false
#| message: false
# Barlett Test Homegenity of Variance: testing for ass
# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
# print(bartlett_test)

@@

# Check Model Assumptions
check_model(model_b, check = c("normality", "homogeneity"))

```{r}
#| echo: false
#| warning: false
#| message: false
# Boxplot to visualize the distribution of `game_after`
ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
  geom_boxplot() +
  ggtitle("Boxplot of Game After Scores by Drug and Dosage Level")

anova_model <- aov(game_after ~ drug + dosage_level, data = clean_data)
summary(anova_model)
# install.packages("ggpubr")
# QQ plot for residuals
ggqqplot(residuals(anova_model))

# Sharpio Test
shapiro.test(residuals(anova_model))
# p-value is greater than 0.05 we fail to reject Ho implies Normality

model_cards_dose <- aov(cards_after ~ drug + dosage_level, data = clean_data)
shapiro.test(residuals(model_cards_dose))
ggqqplot(residuals(model_cards_dose))
```
